On Similarity

### 2016-04-30 paper.tex

Similarity plays a crucial role in psychological theories of knowledge and behaviour, for example, it is used to classify objects \cite{Tversky1977}.
% TODO: maybe, mention \cite{Kriegeskorte2008}
% TODO: a nicer transition
Linguistic treatment of semantic similarity is based on two ideas: word occurrence patterns \emph{define} its meaning \cite{firth1957lingtheory}, while the difference in occurrence \textup{quantifies} the difference in meaning \cite{harris1954distributional}.

>>>>

Similarity plays a crucial role in psychological theories of knowledge and behaviour, for example, it is used to classify objects \cite{hahn1997concepts}.
% TODO: maybe, mention \cite{Kriegeskorte2008}
% TODO: a nicer transition
Linguistic treatment of semantic similarity is based on two ideas: word occurrence patterns \emph{define} its meaning \cite{firth1957lingtheory}, while the difference in occurrence \textup{quantifies} the difference in meaning \cite{harris1954distributional}.
